MSHS COVID-19 Vaccinations

### 2021-03-22 Evening-Huddle-Stats.Rmd
Change format of evening huddle report markdown from having a table of contents to tabs.

---
title: "MSHS COVID-19 Vaccinations"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: TRUE
---

##### Summary as of `r paste(format(Sys.Date(), "%m/%d/%y"), "3:40PM")`

@@

#### All Doses<br>
<p></p>
```{r Subset data and create kable for all doses administered}
all_doses <- system_wide_summary %>%
  filter(Dose == "AllDoses") %>%
  mutate(Dose = NULL)

@@

#### First Doses
<p></p>
```{r Subset data and create kable for first doses administered}
first_doses <- system_wide_summary %>%
  filter(Dose == "Dose1") %>%
  mutate(Dose = NULL)

@@

<p></p>
#### Second Doses
<p></p>
```{r Subset data and create kable for second doses administered}
second_doses <- system_wide_summary %>%
  filter(Dose == "Dose2") %>%
  mutate(Dose = NULL)

>>>>

---
title: "MSHS COVID-19 Vaccinations"
output: html_document
---

@@

#### Administered & Scheduled Vaccines as of `r format(Sys.Date(), "%m/%d/%y")` 3:40PM {.tabset}

##### All Doses
```{r Subset data and create kable for all doses administered}
all_doses <- system_wide_summary %>%
  filter(Dose == "AllDoses") %>%
  mutate(Dose = NULL)

@@

##### First Doses
<p></p>
```{r Subset data and create kable for first doses administered}
first_doses <- system_wide_summary %>%
  filter(Dose == "Dose1") %>%
  mutate(Dose = NULL)

@@

<p></p>
##### Second Doses
<p></p>
```{r Subset data and create kable for second doses administered}
second_doses <- system_wide_summary %>%
  filter(Dose == "Dose2") %>%
  mutate(Dose = NULL)
